Proposed Solution

### 2017-01-23 CAV17/secs/postanal.tex
expand post-analysis section

VeriConf can output the set of learned rules from the training set as described in $\S$\ref{sec-learn}.
Note that the ability to inspect the learned rule set is a special property of this technique.
The core task, building a model from unlabeled examples to classify files as either correct or incorrect, is also a classic problem for other machine learning techniques such as neural networks~\cite{nn1,nn2,nn3}.
When applying machine learning to verification of configuration files, this is not, however, an ideal approach.
The resulting model from a neural network is easily not amenable to analysis~\cite{nnAnalysis1,nnAnalysis2}.
The simple structure of rules with weights from an association rule learning-like approach, will instead allows us to do further inference on the resulting model.

@@

    $$w = \frac{true - false}{total}$$

@@

@@

\para {Semantics}
Intuitively, keywords that are seen together more often with defined relationships are more likely to generate rules within the learner.
 (it would be nice to show this with a quick derivation)

@@

@@

@@

>>>>

VeriConf can output the set of learned rules from the training set as described in $\S$\ref{sec-learn}.
Note that the ability to inspect the learned rule set is a special property of this technique.
The core task, building a model from unlabeled examples to classify files as either correct or incorrect, is also a classic problem for other machine learning techniques such as neural networks~\cite{nn1,nn2,nn3}.
When applying machine learning to verification of configuration files, this is not, however, an ideal approach.
The resulting model from a neural network is not easily amenable to analysis~\cite{nnAnalysis1,nnAnalysis2}.
The simple structure of rules with weights from an association rule learning-like approach, will instead allows us to do further inference on the resulting model.

@@

    $$w = \frac{true}{total}$$

@@

\iffalse

\fi

\para {Semantics}

@@

Note that since the Rule Graph, as it is formulated in this paper, weights edges
by a {\it ratio} of predicate hits to total keyword observations, the weight
of an edge is {\bf dependent only on the confidence of the corresponding rule
and independent of the support}. We address this issue by pruning nodes of
inadequate support in the learner, but an alternative formulation of the rule
graph (in particular the  of edges in the graph) may provide additional
power for graph analysis techniques to take support into account
as well as confidence.

\rahul{Not sure how important this last point about alternative Rule Graph
formulation is - we certainly want to make sure the reader understands that
this is an area that can be easily expanded on, but don't want to distract
from the fundamental semantics here.}

It is also worth noting that how good of a heuristic the $DEGREE$ metric is for
\"importance of a configuration parameter\" is dependent on the coverage
of the learnable predicate set encompassed by $L$. The more this predicate
set covers the true configuration parameter relationships in the system,
the better the heuristic.

\iffalse

Intuitively, keywords that are seen together more often with defined relationships are more likely to generate rules within the learner.
 (it would be nice to show this with a quick derivation)

@@

\fi

@@

A common goal for software projects is managing complexity. As
constraints accumulate over the lifecycle of a project additional
configuration file complexity often grows, with the danger of
making code brittle and unwieldy. For code, Kolomogrov complexity
can be a good indicator of whether a solution is bloated and 
needs to be refactored.

The intermediate representation produced VeriConf's learner stage
may be used to analyze the complexity of a configuration file.

@@

\iffalse

Use the listing in figure 2 to put together an example of why the
naive implementation of complexity doesn't give as much of an idea
of what is going on as our heuristic.

\fi
